---
title: "NSDP Data Processing"
author: "Rara Soro"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output: 
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: '2'
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Library, echo = FALSE, warning=FALSE, message=FALSE}
library(knitr) # Nice tables
library(kableExtra) # Extra nice tables
library(dplyr) #Calculation and other functions
```

## Introduction

The Vanuatu National Statistics Office (VNSO) undertook the extended Household Income and Expenditure Survey (HIES) for a period of 12 month and was refered to as National Sustainable Development Plan (NSDP) Baseline Survey.

C:\RTraining\Repositories\nsdp-R-processing\NSDP-Data-Processing

```{r Setting working directory, echo = FALSE, eval=FALSE}
wd <- file.path("c:", "RTraining", "Repositories", "nsdp-R-processing", "NSDP-Data-Processing")
setwd(wd)

```

```{r Load Dataset, echo=FALSE}
nsdp_data <- read.csv(file.path("data", "cover.csv"), header = TRUE)
head(nsdp_data)
nsdp_dem <- read.csv(file.path("data", "demography.csv"), header = TRUE)
head(nsdp_dem)

```

## Basic Statistics
### Number of Household by Province
```{r Basic HHStatistics, echo=FALSE, warning=FALSE}
nsdp_tab1 <- nsdp_data %>%
  group_by(id1_Province) %>%
  summarize(Total_Household = round(sum(fweight)))


kable(nsdp_tab1)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "border", "condensed", "responsive")) %>%
  kable_styling(font_size = 10) 
```


### Population by Province
```{r Basic Population Statistics, echo=FALSE, warning=FALSE}
nsdp_tab2 <- nsdp_dem %>%
  group_by(id1_Province) %>%
  summarize(Total_Population = round(sum(fweight)))


kable(nsdp_tab2)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "border", "condensed", "responsive")) %>%
  kable_styling(font_size = 10) 
```



